|

### 2023-05-12 paper/00-main.Rmd
added defensive formation figure

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.pos = "p",
  cache = TRUE
)
library(here)
```

>>>>

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.pos = "p",
  cache = TRUE
)
library(here)
library(tidyverse)
```

### 2023-05-12 paper/01-introduction.Rmd
added defensive formation figure

We limit our attention in this manuscript to the defensive side of the ball. There are two main types of defensive linemen in American football: (1) defensive tackles (DTs) located within the interior of the line and (2) defensive ends (DEs) located along the edges (see Figure INSERT FIGURE NUMBER HERE for example formation with DTs and DEs). The primary purpose of both positions is to rush the QB on passing plays, with DEs displaying superiority in observed pass rushing ability [@Eager2018nfl]. Additionally, within DTs there are nose tackles (NTs) who directly line up across from the ball at the line of scrimmage (see Figure INSERT FIGURE NUMBER HERE for example defensive formation with a NT). Typically, teams will employ either one NT or two DTs on the interior with DEs along either side of the defensive line. In addition to defensive lineman, other positions may attempt to rush the QB on blitzing plays such as outside linebackers (OLBs), interior linebackers (ILBs), and potentially members of the secondary (cornerback, free safety, strong safety) who typically play pass coverage.

INSERT FORMATION FIGURE X

INSERT FORMATION FIGURE Y

>>>>

We limit our attention in this manuscript to the defensive side of the ball. There are two main types of defensive linemen in American football: (1) defensive tackles (DTs) located within the interior of the line and (2) defensive ends (DEs) located along the edges (see Figure \ref{fig:formation} (top) for example formation with DTs and DEs). The primary purpose of both positions is to rush the QB on passing plays, with DEs displaying superiority in observed pass rushing ability [@Eager2018nfl]. Additionally, within DTs there are nose tackles (NTs) who directly line up across from the ball at the line of scrimmage (see Figure \ref{fig:formation} (bottom) for example defensive formation with a NT). Typically, teams will employ either one NT or two DTs on the interior with DEs along either side of the defensive line. In addition to defensive lineman, other positions may attempt to rush the QB on blitzing plays such as outside linebackers (OLBs), interior linebackers (ILBs), and potentially members of the secondary (cornerback, free safety, strong safety) who typically play pass coverage.

```{r formation, fig.width=5, fig.height=4, fig.cap="Two common defensive alignments in football: 4-3 defense (top) and 3-4 defense (bottom). The dashed line represents the line of scrimmage separating the defense and offense."}
tibble(x = c(3:5, 3:6 - 0.5, c(2, 3.7, 4.3, 6)),
       y = c(1, 1, 1, 1.01, 1.01, 1.01, 1.01, 1.02, 1.02, 1.02, 1.02),
       pos = c("DE", "NT", "DE", "OLB", "ILB", "ILB", "OLB",
               "CB", "S", "S", "CB"),
       d = "3-4 Defense") |> 
  bind_rows(
    tibble(x = c(3:6, c(2.5, 4.5, 6.5), c(2, 4.1, 4.9, 7)),
           y = c(1, 1, 1, 1, 1.01, 1.01, 1.01, 1.02, 1.02, 1.02, 1.02),
           pos = c("DE", "DT", "DT", "DE", "OLB", "MLB", "OLB",
                   "CB", "S", "S", "CB"),
           d = "4-3 Defense") 
  ) |> 
  mutate(d = fct_relevel(d, "4-3 Defense", "3-4 Defense")) |> 
  ggplot(aes(x, y)) +
  geom_tile(fill = "white") +
  geom_label(aes(label = pos), size = rel(4)) +
  geom_hline(yintercept = 0.996, linetype = "dashed") +
  facet_wrap(~ d, scales = "free", ncol = 1) +
  coord_cartesian(ylim = c(0.99, 1.03)) +
  theme_light() +
  theme(strip.text = element_text(size = rel(1.2)),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())
```

### 2023-05-12 paper/04-results.Rmd
added defensive formation figure

```{r}
#| label: fig_rankings_boot
#| fig.cap: "Top 10 pass rushers for each position (DE, DT, NT, OLB) by mean varying intercept with 95% confidence intervals."
#| fig.width: 6
#| fig.height: 8
source(here("scripts", "10_multilevel_mod.R"))
fig_rankings_boot
```

>>>>

```{r}
#| label: fig_rankings_boot
#| fig.cap: "Top 10 pass rushers for each position (DE, DT, NT, OLB) by mean varying intercept with 95\\% confidence intervals."
#| fig.width: 6
#| fig.height: 8
source(here("scripts", "10_multilevel_mod.R"))
fig_rankings_boot
```
